A Simple Minibatch Acceptance Test for MCMC

### 2016-05-20 nips_2016.tex
Improved the theoretical explanation a tiny bit.

We use some additional terms from standard Markov chain theory~\cite{Meyn2009}. Let the
\emph{transition kernels} of MCMC on complete and minibatch data at step $i$ be $P_i$ and $P_i'$,
respectively. When these kernels (e.g., $P_i$) are applied on a probability distribution $D_1$, they
generate a new distribution $D_2$, which we write as $P_i \circ D_1 = D_2$. Define $\pi$ to be the
stationary distribution obtained by $P_i$, and $\pi_i'$ to be the stationary distribution obtained
by $P_i'$.  Finally, we indicate the \emph{total variation distance} between two kernels using $\|
\cdot \|$, e.g., $\|P_i-P_i'\|$.

@@

Since ${\rm Var}(\Delta') < 4\epsilon^2 k^2 (m - \frac{m(m-1)}{N-1}) $, we can assume the maximum
value of $X_{\xi}$ is proportional to the standard deviation of $\Delta'$, i.e. $\epsilon$. Thus, we
can assume $\zeta=\epsilon C$, where $C$ is a constant factor.

We finally introduce Theorem~\ref{thm:theory3} to characterize the convergence of our samples.

\begin{theorem}\label{thm:theory3}
Assume $\pi$ satisfies $\|P_i \circ D_0 - \pi\| \leq \eta \|D_0 - \pi\|$, where $\eta \in [0, 1)$ for
all distributions $D_0$. Also assume there exists $0 < \rho_t < 1$ such that $\|P'_i(x, \cdot) -
\pi_i'\| \leq 2\rho_i$. We can get $\| P_t' \circ P_{t-1}' \circ \cdots \circ P_1' \circ D_0 - \pi
\| \leq \sum_{s=1}^t \{\prod _{u=s+1}^t \rho_u (1-\alpha_u)\} \rho_s \alpha_s + \alpha_t $, where
$\alpha_i = \frac{\epsilon_i C }{1-\eta}$.
\end{theorem}

>>>>

We use some terms from standard Markov chain theory~\cite{Meyn2009}. Let the \emph{transition
kernels} of MCMC on complete and minibatch data at step $i$ be $P_i$ and $P_i'$, respectively. When
these kernels (e.g., $P_i$) are applied on a probability distribution $D_1$, they generate a new
distribution $D_2$, which we write as $P_i \circ D_1 = D_2$. Define $\pi$ to be the stationary
distribution obtained by $P_i$, and $\pi_i'$ to be the stationary distribution obtained by $P_i'$
($\pi'$ needs a subscript in this case).  Finally, we indicate the \emph{total variation distance}
between two kernels using $\| \cdot \|$, e.g., $\|P_i-P_i'\|$.

@@

Since ${\rm Var}(\Delta') < 4\epsilon^2 k^2 (m - \frac{m(m-1)}{N-1}) $, we can assume the maximum
value of $X_{\xi}$ is proportional to the standard deviation of $\Delta'$, i.e. $\epsilon$. Thus, we
can assume $\zeta=\epsilon C$, where $C$ is a constant factor. We finally introduce
Theorem~\ref{thm:theory3} to characterize the convergence of our samples.

\begin{theorem}\label{thm:theory3}
Assume $\pi$ satisfies $\|P_i \circ D_0 - \pi\| \leq \eta \|D_0 - \pi\|$, where $\eta \in [0, 1)$ for
all distributions $D_0$. Also assume there exists $0 < \rho_t < 1$ such that $\|P'_i(x, \cdot) -
\pi_i'\| \leq 2\rho_i$. We can get $\| P_t' \circ P_{t-1}' \circ \cdots \circ P_1' \circ D_0 - \pi
\| \leq \sum_{s=1}^t \{\prod _{u=s+1}^t \rho_u (1-\alpha_u)\} \rho_s \alpha_s + \alpha_t $, where
$\alpha_i = \frac{\epsilon_i C }{1-\eta}$ and $\epsilon_i$ is the step size at iteration $i$.
\end{theorem}
